\documentclass{ies2018}
\usepackage{amsmath}
\usepackage{graphicx}


%% Put title here
\title{Paper for IES2018}

%% List authors here
\author{John Doe $^{\dagger}$ \and Jane Doe $^{\ddagger}$}
%% Authors' affiliations
\affiliation{%
    ${}^\dagger$ University/Company, City, Country\\
    ${}^\ddagger$ University/Company, City, Country
}
%% Contact email address
\email{corresponding.author@email.address}

%% Put abstract here
\abstract{%
    This is the \LaTeXe template for IES2018 in Sapporo, Japan.
    The authors should prepare the manuscript of your paper based on the format this paper shows, and submit in accordance with the guidance provided in the web site: \url{http://autonomous.jp/ies2018/submissions/}
}%
%% with relevant keywords
\keywords{At least three keywords relevant to your work}


\begin{document}

\maketitle

\section{Welcome}
The Asia-Pacific Symposium on INTELLIGENT AND EVOLUTIONARY SYSTEMS first took place in 1997 in Canberra and since then, the Asia-Pacific IES Symposiums have become prestigious incubators of research ideas, as well as facilitators of research collaboration.
The Symposiums aim to bring together researchers and practitioners from countries of Asia-Pacific Region in the field of intelligent systems and evolutionary computation to present ongoing work, exchange ideas, and discuss future collaboration.
Researchers from elsewhere interested in collaboration with researchers from the Asia-Pacific Region are most welcome.

The 22nd edition of the conference, {\bf IES 2018}, will be held in Sapporo, Japan, during December 20-22, 2018, and organized by Hokkaido University.

{\bf IES 2018} welcomes fundamental science, methodology method, and practical application papers in the IES Symposiums' traditional range of topics, which includes but is not limited to:
\begin{itemize}
    \item Artificial Intelligence
    \item Artificial Life and Societies
    \item Machine Learning
    \item Neural Networks
    \item Data Science ans Decision Analytics
    \item Evolutionary and Nature Inspired computation
    \item Game Theory
    \item Human/Brain-Computer Interaction
    \item Agents and Complex Systems
    \item Cognitive and Developmental Systems
    \item Robotics Systems
    \item Collective Intelligence
    \item Swarm Systems
    \item Intelligent Transport Systems
\end{itemize}

\section{Paper submission}
The paper size must be A4, and it should be typed in two columns with single spacing.
All of contents including the list of references should be put in {\bf xx} to {\bf xx} pages.

\begin{thebibliography}{99}
    \bibitem{item1}
        Author,
        ``Paper title'',
        Journal name,
        Vol. 0, No. 0, pp. 1--42, 2018.
\end{thebibliography}

\end{document}
